Labor Market Income and Substitution Effects Explain Contemporary Natural Selection

### 2020-12-16 why-negative-selection.Rmd
Tweaks

res_combined %>% 
      mutate(
        score_name = pretty_names(score_name),
        score_name = fct_reorder(score_name, estimate, order_abs(2)),
        Regression = ifelse(reg.type == "raw", "Uncontrolled", "Controlled for AFLB")
      ) %>% 
      rename(p = p.value) %>% 
      ggplot(aes(y = score_name, x = estimate, fill = Regression, 
        color = p < 0.05/{{n_regs}})) + 
        my_vline +
        pval_geom_point() +
        pval_scale() +
        my_fill_scale(n = 2, direction = -1) +
        my_labs() +
        my_theme()
```

@@

```{r plot-cors-earnings-educ, fig.cap="Selection effects, with and without controls for age at first live birth, by correlations with earnings and educational attainment. Each point represents one PGS."}

>>>>

res_combined %>% 
      mutate(
        score_name = pretty_names(score_name),
        score_name = fct_reorder(score_name, estimate, order_abs(2)),
        Regression = ifelse(reg.type == "raw", "Uncontrolled", "Controlled for AFLB")
      ) %>% 
      rename(p = p.value) %>% 
      ggplot(aes(y = score_name, x = estimate, fill = Regression, 
        color = p < 0.05/{{n_regs}})) + 
        my_vline +
        pval_geom_point() +
        pval_scale() +
        my_fill_scale(n = 2) +
        my_labs() +
        my_theme()
```

@@

```{r plot-cors-earnings-educ, fig.cap="Selection effects, with and without controls for age at first live birth, by correlations with earnings and educational attainment. Each point represents one PGS.", fig.height = 4}
